---
title: "LidR Segmentation Script"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a documentation of the processes required to create a segmented image, along with some of the equations necessary to find individual trees.

First, the following libraries must be installed.
```{r}
library(lidR)
if (!require("lidR")) {
  install.packages("lidR")
  library('lidR')
}
if (!require("rgdal")) {
  install.packages("rgdal")
  library('rgdal')
}
if (!require("dplyr")) {
  install.packages("dplyr")
  library('dplyr')
}
if (!require("ggplot2")) {
  install.packages("ggplot2")
  library('ggplot2')
}
if (!require("rjson")) {
  install.packages("rjson")
  library('rjson')
}
if (!require("bitops")) {
  install.packages("bitops")
  library('bitops')
}
if (!require("jsonlite")) {
  install.packages("jsonlite")
  library('jsonlite')
}
if (!require("leaflet")) {
  install.packages("leaflet")
  library('leaflet')
}
if (!require("RCurl")) {
  install.packages("RCurl")
  library('RCurl')
}
if(!requireNamespace("EBImage"))
  BiocManager::install("EBImage")
  library("EBImage")
```


Once done, a file path must be set. In this case, this is the example.las file used, however, a different file type can be used, by ignoring portions of text(most of it, in fact)

```{r}
file_path = "/home/rstudio/keys/code/Example.las"
las = readLAS(file_path)
```
With an las, once read, the following code needs to be run in order to normalize and classify ground points.
```{r}
las = lasground(las, csf())
plot(las, color = "Classification")
las = lasnormalize(las, tin())
```
Here, we'll define the algorithm used for the CHM made from the las.
```{r}
algo = pitfree(thresholds = c(0,10,20,30,40,50), subcircle = 0.2)
chm  = grid_canopy(las, 0.5, algo)
```

Now, we have a raster, chm, which has a height-corrected map of our las. Once found, we can segment this, convert to polygons, and apply the countour.
```{r}
crowns = watershed(chm)()
plot(crowns, col = pastel.colors(100))
```
```{r}
contour = rasterToPolygons(crowns, dissolve = TRUE)
plot(contour)
```
This is just the outlines. Here are both, overalyed.
```{r}
plot(chm, col = height.colors(50))
plot(contour, add = T)
```
